\chapter{Conclusion and Recommendation}
\section{Conclusion}
Cybersecurity is a complex field and threat actors are ever evolving their trade-craft in clever ways. Every single
running business is not too small to be attacked, but they may be too small for them to make the news. Therefore, transparency
to the clients is important, because lack of visibility to the clients can lead to a loss of trust. This graduation project serves as the
first iteration by \acrshort{qict} about the integration of SentinelOne to its internal application, the \acrshort{qaas} app.

SentinelOne \acrshort{edr} platform is possible to be integrated with the \acrshort{qaas} app, which was made in Flutter with
Firebase as the back-end cloud solution, utilizing SentinelOne \acrshort{api} to fetch the data. In order that this \acrshort{api}
to be able to send the correct data, the necessary Agents and Ranger need to be set up properly in a client's machine. This Agent will then serve
to replace the traditional \acrshort{av}, as it will gather the data from the client's machine and send it to the management database, providing real-time
monitoring. Additionally, a SentinelOne account with the necessary rights to read the data with its \acrshort{api} key is also needed to be configured. In the
front-end, the visualization is done using the Flutter package: \textit{fl\_chart} and \textit{syncfusion\_flutter\_charts}. The \acrshort{qaas} app itself has 3
different user roles in its system: the clients, the helpdesk, and the \acrshort{it} admins. The objective of this project is that for the \acrshort{qaas} app to
be used by the clients to see the status of their devices, and the helpdesk and \acrshort{it} admins to manage and monitor the client devices that are connected to
the SentinelOne \acrshort{edr} platform. For the client user, they can see the status of their devices that are connected to the SentinelOne \acrshort{edr}
The user itself can customize which charts and data they want to see in the dashboard,
to make it more user-friendly and catching up with other \acrshort{edr} platforms. The user can also see the details of the
threats that are detected by SentinelOne, and the user can also see the details of the devices that are connected to the SentinelOne
\acrshort{edr} platform.

In the back-end, several functions with different functionalities need to be created to handle the data that is fetched from different SentinelOne
\acrshort{api} endpoints. The user's session and preference data are stored in the Firebase Firestore database, and as well as \acrshort{ai} powered
Algolia search engine to make the search faster and more accurate. Additional features such as filtering, sorting, and pagination will be handled by
inputting the correct headers to the \acrshort{api} request.

\section{Recommendation}

% Modules issue
There are some issues that the author has noticed with the way the \acrshort{qaas} app code was structured. For example, when
assigning modules to a user,

% N-Central API issue: Not all data is correct

% API monitoring