\chapter{Research Design}

\section{Research Topic}
In research, it is paramount to have the formulation of a clear research topic, research main question,
and research sub-questions. The main question serves as the focal point around which the research revolves,
encapsulating the primary objective or purpose of the study.
The following main research question will be used throughout the research:
\addcontentsline{toc}{subsection}{How can Quality ICT B.V. effectively integrate and leverage SentinelOne EDR platform
      for continuous cybersecurity monitoring?}
\begin{center}
      \textit{"How can Quality ICT B.V. effectively integrate and leverage SentinelOne EDR platform
            for continuous cybersecurity monitoring in their internal web application, the QaaS App?"}
\end{center}
\section{Research Sub-Questions}
The research sub-questions are then used to function as a pathway that dissects the main
question into smaller, more manageable components, which can then be addressed individually. This approach
allows for a more comprehensive and in-depth analysis of the research topic, ensuring that all relevant
aspects are covered and that the research is conducted in a systematic and organized manner.
This research main question is therefore expanded in the following research sub-questions:
\addcontentsline{toc}{subsection}{Sub-question \#1: What are the primary technologies and components utilized in the QaaS web
      application, and how do they function together to operate the system, including both front-end and back-end infrastructure?}
\addcontentsline{toc}{subsection}{Sub-question \#2: What technologies and components underpin the SentinelOne EDR platform
      as one of the leading cybersecurity solution?}
\addcontentsline{toc}{subsection}{Sub-question \#3: Is the integration of SentinelOne into the QaaS app
      environment possible and how can it be done?}
\addcontentsline{toc}{subsection}{Sub-question \#4: What are the best visualization techniques to display
      the SentinelOne data to the users in the QaaS App?}
\begin{enumerate}
      \item What are the primary technologies and components utilized in the \acrshort{qaas} web application, and how do they function
            together to as a system, including both front-end and back-end infrastructure?
      \item What technologies and components underpin the SentinelOne EDR platform as one of the leading cybersecurity solution, and how
            does its integration enhance the cybersecurity monitoring capabilities of the \acrshort{qaas} App?
      \item Is the integration of SentinelOne into the \acrshort{qaas} app environment possible and how can it be done while still
            utilizing their key features and capabilities in context of cyber-threat detection and remote \acrshort{it} infrastructure
            management?
      \item What are the best visualization techniques to display the SentinelOne data to the users to ensure clear and insightful
            representation of threats?
\end{enumerate}
\section{Research Methodology}
In this research, different research methods have been used to answer the research questions. This research
will be based on the six \acrshort{ict} research methods defined by HBO-I (\cite{ictresearchmethods}). A
research method for each sub-question is then defined along with how the results are considered valid and
reliable:
\subsection{Method of Data Collection}
\begin{itemize}[label=-]
      \item Sub-question \#1: desk research of Literature Study will be conducted, with the goal of creating
            infrastructure information that displays the structure of the \acrshort{qaas} app and all its
            dependencies. Furthermore, Interview with key stakeholders involved in the  development, maintenance,
            and usage of the \acrshort{qaas} app will be conducted to gain insights into the current situation
            of the app. Analysis on the current \acrshort{qaas} app and its capabilities.
      \item Sub-question \#2: information gathering through various reliable source on the Internet, such as
            Gartner and Wikipedia.
            % Literature Study on various articles on the Internet, interviews, expert reviews,
            % and requirement elicitation techniques such as use case analysis and user stories. 
      \item Sub-question \#3: technical assessments and will be conducted, under the supervision of the Company
            Supervisor, to evaluate the technical feasibility, compactibility, and alignment of SentinelOne's
            features with the \acrshort{qaas} app environment.
      \item Sub-question \#4: research into existing visualization techniques for \gls{JSON} data coming from
            SentinelOne \acrshort{api} through Literature Study. Analyze existing data visualization tools and
            platforms that are available in Flutter and Firebase. Gather requirements from project stakeholders
            regarding data visualization preferences and usability and do data analysis and usability testing.
            % \item Sub-question \#4: technical evaluations of SentinelOne's capabilities and \acrshort{api}s will
            %       be conducted, the \acrshort{api} documentation and integration guideline will be read and review
            %       with Literature Study method and case studies of similar integrations. Requirements from the
            %       cybersecurity experts from the \acrshort{qict} department responsible for SentinelOne's technical
            %       support will be gathered and analyzed. Furthermore, Prototyping with proof-of-concept prototypes
            %       on a test environment will be conducted to test different integration scenarios, assess feasibility,
            %       identify potential challenges, refine the approach, and evaluate the performance of the integration.
\end{itemize}
\subsection{Selected Measuring Instruments}
\begin{itemize}[label=-]
      \item Sub-question \#1: structured interview guide, document report checklist analysis and review,
            observation, analysis tools for codebase and logs, and quite possibly supplemented by surveys
            or questionnaires.
      \item Sub-question \#2: document analysis tools for literature review. Structured questionnaires for
            requirement interviews regarding functionality rating scale and compare the response against
            industry standards and best practices. Observation of existing \acrshort{api} monitoring tools.
            Prioritize functionalities based on importance, feasibility, and impact on the \acrshort{qaas} app.
      \item Sub-question \#3: technical assessments and requirement workshops will be conducted. Furthermore,
            \acrshort{api} documentation  review, document analysis tools, security impact risk assessment,
            and feasibility checklist assessment with the Company Supervisor will also be overseen.
      \item Sub-question \#4: the selected measuring instruments for this sub-question will be through
            observation of existing data visualization tools, literature review through reading the studies of
            the best visualization suitability matrix techniques, structured questionnaires to end-user
            interviews, and usability testing heuristics.
\end{itemize}
\subsection{Method of Data Analysis}
\begin{itemize}[label=-]
      \item Sub-question \#1: a qualitative thematic \acrshort{swot} analysis of interview transcripts
            and documentation for operational insights to identify strengths, weaknesses, and areas for
            improvement in the current situation of the \acrshort{qaas} app.
      \item Sub-question \#2: comparative analyze survey/interview responses using \acrshort{mcda} and
            compare against industry standards and best practices. Prioritize functionalities based on
            importance, feasibility, and impact on the \acrshort{qaas} app.
      \item Sub-question \#3: evaluate the technical feasibility, compactibility, and alignment of
            SentinelOne's features with the \acrshort{qaas} app environment. Analyze potential integration
            challenges and mitigation strategies and assess the performance of the integration through
            prototyping and testing. Technical analysis for the \acrshort{api} documentation and
            thematic analysis for interview data.
      \item Sub-question \#4: technical tool analysis by reviewing and evaluating the suitability of different
            visualization techniques for representing the data processed and received by the \acrshort{qaas}
            app in \acrshort{xml} and \acrshort{json} formats from the \acrshort{api} considering factors such
            as clarity, interpretability, and user engagement. Do a user-centered design and cognitive load
            analysis by analyzing feedback from company stakeholders, supervisor, and end-users.
\end{itemize}
\subsection{Reliability, Validity, and General Applicability}
\begin{itemize}[label=-]
      \item Sub-question \#1: the reliability of the data can be ensured by triangulation of data from
            multiple sources and conducting interviews with stakeholders from different departments with
            structure questionnaires to ensure that the data is consistent and accurate. The validity of
            the data will be ensured by  cross-referencing with the existing literature or industry best
            practices or other sources and  through information obtained from  interviews with the
            \acrshort{qaas} app developers to ensure  that the data is accurate and reliable. The general
            applicability of the data will be ensured by  ensuring that the information obtained is relevant
            and applicable to the research question and  that it can be used to draw meaningful conclusions
            and make informed decisions, furthermore by comparing findings with industry standards and best
            practices or similar case studies or projects.
      \item Sub-question \#2: ensure reliability through sampling techniques and representative stakeholder
            involvement, with comprehensive literature review and multiple sources of information. Validate
            priorities against real-world scenarios or case studies involving diverse expert panel, like
            the Company Supervisor. General applicability can be assessed by comparing prioritization with
            similar projects or frameworks and considering scalability and adaptability of the integration
            with representative user samples.
      \item Sub-question \#3: the validity of this sub-question will be through pilot integration unit testing
            or proof of concept documents and ensuring alignment with cybersecurity standards and best
            practices. The reliability will be to consider future needs such as adaptability and scalability of
            the integration, and focus on \acrshort{qict} user context and needs. General applicability can be
            assessed by comparing integration strategies with industry standards or expert opinions such as from
            the Company Supervisor.
      \item Sub-question \#4: reliability can be defined by ensuring future adaptability with comprehensive
            literature review and multiple sources of information. Validity can be achieved through validating
            visualization choices through data-driven approach in usability testing or  prototyping, ensuring
            alignment with best practices in data visualization and involving the expert, like the Company
            Supervisor on the field. General applicability can be assessed by accessibility considerations by
            comparing proposed visualization techniques with similar applications or domains.
\end{itemize}
\subsection{Research Limitations}
The project and research in general will be limited on the \acrshort{api} request methods, in which the author
is allowed to do only GET requests. This is due to the fact that the author is not allowed to do any PATCH,
POST, PUT, DELETE, or any other \acrshort{http} request methods that could potentially change the data in SentinelOne data records.
This limitation is because the author is not a full-time employee of \acrshort{qict} and is not allowed to make any changes to the
\acrshort{qaas} app or the \acrshort{api} that is being requested, and the nature of the project is to only show data to the users and
not give access for them to change the data. Therefore, the author is limited to do research in the best practices of SentinelOne
integration for the GET request method only. Furthermore, given that the main purpose of this project is to only show data to the
users rather than facilitate data editing - it is determined that permissions for GET requests alone are necessary.

During the realization part of this project, the author will be given access to the test environment in both Firebase and the Flutter
codebase. This setup allows the author to do extensive experimentation with the design, the database, and the cloud functions without
compromising the integrity of the live application. Upon completion of the development phase and thorough bug resolution, the project
will undergo a staged migration to the live environment. Initially, the deployment will be restricted to the Preview channel of the live
version, thereby preventing public accessibility at this juncture.

In this intermediate stage, the author, in collaboration with the Company Supervisor, will conduct a comprehensive review of
the application. Mainly, they will make sure the application functions correctly across various customer accounts from different companies.
It involves verifying that users can only access their designated data, thus maintaining strict user access controls and permissions.
Additionally, the check encompasses aspects such as responsiveness, accuracy in spelling, bug resolution, and the functionality of all
features, among others This critical evaluation will then ensure the application's readiness for its eventual launch in the live
environment, where it will be accessible to customers and employees of \acrshort{qict}, like the helpdesk, cybersecurity specialists,
the stakeholder and other  software developers. It is important to note that this phased approach does not impede the execution of
sub-questions 3 and 4 of this project.

Sub-question 3 addresses the integration of SentinelOne into the \acrshort{qaas} App environment. The focus here is on leveraging
SentinelOne's functionality in regard to the main objective of this project. This means showing data related cyber-threat detection and
remote \acrshort{it} infrastructure management within the constraints of the \acrshort{qaas} App platform.

Sub-question 4 explores the optimal visualization techniques for presenting data obtained through the SentinelOne \acrshort{api} in
Flutter-based application. The objective is to ensure that the representation of security threats is both clear and informative, setting a
benchmark against other security threat platforms. Therefore, \acrshort{api} request such as POST, PUT, DELETE, or PATCH are not necessary for
this research.

The author is also limited in showing the SentinelOne dashboard data, as it contains clients' sensitive
information, and \acrshort{qict} has over 400 clients. Therefore, if any part of the SentinelOne dashboard is
shown, it will be with blurred sensitive information.

Moreover, the author is also limited to the non-disclosure agreement signed within the initialization period of
the graduation work placement. This means that any confidential information that the company deems as confidential
will not be disclosed in this research. This includes any information that is not publicly available, such as any
financial data or security data pertaining to the internal system or the \acrshort{qaas} app internal code.

It is also crucial to note that these limitations also do not undermine the overall scope of the research. The
primary objectives remain focused on assessing the feasibility of integration and demonstrating the process involved.
